Comparing Predicted Boundaries vs Called Boundaries

### 2019-08-28 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
editted barplots

pred_v_called_10_df <- data.frame(LogDist = c(#Predicted
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1),
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[2]]))$distance+1),
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[3]]))$distance+1),
    log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[4]]))$distance+1),

    #Called
    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1),
    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[2]]))$distance+1),
    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[3]]))$distance+1),
    log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[4]]))$distance+1)
),
Annotation = c(#Predicted
    rep("CTCF",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("RAD21",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("SMC3",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("ZNF143",length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),

    #Called
    rep("CTCF",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
    rep("RAD21",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
    rep("SMC3",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
    rep("ZNF143",length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))),
BoundReg = c(#Predicted
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),
    rep("Predicted", length(log2(mcols(distanceToNearest(all_pred_bounds, annots.GR.f[[1]]))$distance+1))),

    #Called
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1))),
    rep("Called", length(log2(mcols(distanceToNearest(all_true_bounds_r, annots.GR.f[[1]]))$distance+1)))))

pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("Predicted", "Called"))

ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
    facet_grid(~ Annotation) +    
    stat_boxplot(geom ='errorbar', width = 0.2) + 
    geom_boxplot(outlier.shape = NA) +
    geom_signif(test = "wilcox.test", 
                comparisons = list( c("Predicted", "Called")),
                vjust = 0,
                textsize = 4,
                size = .5,
                step_increase = .08,
                color="black") +
    theme_minimal()+
    theme_bw()+
    ylab("Log2 Distance to Annotation")+
    xlab("") +
    scale_fill_manual(name="Boundary Region",
                      values=c("red",
                               "blue"))+
    scale_color_manual(values=c("red",
                                "blue")) +
    guides(color=FALSE, linetype=FALSE)+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          strip.text.x = element_text(size = 15),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=15),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")
```

>>>>

#predicted but not called
pbnc <- all_pred_bounds[-unique(subjectHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]

#called and predicted
cap1 <- all_pred_bounds[unique(subjectHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]
cap2 <- all_true_bounds_r[unique(queryHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]
cap <- GRangesList(cap1,cap2)
cap <- do.call("c", cap)

#called by not predicted
all_true_bounds2 <- all_true_bounds[-unique(queryHits(findOverlaps(all_true_bounds,all_pred_bounds_r)))]
cbnp <- resize(all_true_bounds2, width=1,fix = "center")

pred_v_called_10_df <- data.frame(LogDist = c(#PBNC
    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1),
    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[2]]))$distance+1),
    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[3]]))$distance+1),
    log2(mcols(distanceToNearest(pbnc, annots.GR.f[[4]]))$distance+1),

    #CAP
    log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1),
    log2(mcols(distanceToNearest(cap, annots.GR.f[[2]]))$distance+1),
    log2(mcols(distanceToNearest(cap, annots.GR.f[[3]]))$distance+1),
    log2(mcols(distanceToNearest(cap, annots.GR.f[[4]]))$distance+1),

    #CBNP
    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1),
    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[2]]))$distance+1),
    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[3]]))$distance+1),
    log2(mcols(distanceToNearest(cbnp, annots.GR.f[[4]]))$distance+1)
),
Annotation = c(#pbnc
    rep("CTCF",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
    rep("RAD21",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
    rep("SMC3",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
    rep("ZNF143",length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),

    #cap
    rep("CTCF",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
    rep("RAD21",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
    rep("SMC3",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
    rep("ZNF143",length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),

    #cbnp
    rep("CTCF",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
    rep("RAD21",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
    rep("SMC3",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
    rep("ZNF143",length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1)))),
BoundReg = c(#pbnc
    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),
    rep("PBNC", length(log2(mcols(distanceToNearest(pbnc, annots.GR.f[[1]]))$distance+1))),

    #cap
    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),
    rep("CAP", length(log2(mcols(distanceToNearest(cap, annots.GR.f[[1]]))$distance+1))),

    #cbnp
    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1))),
    rep("CBNP", length(log2(mcols(distanceToNearest(cbnp, annots.GR.f[[1]]))$distance+1)))))

pred_v_called_10_df$BoundReg <- factor(pred_v_called_10_df$BoundReg, levels=c("PBNC", "CAP", "CBNP"))

ggplot(pred_v_called_10_df, aes(x=BoundReg, y = LogDist, fill=BoundReg, color=BoundReg))  + 
    facet_grid(~ Annotation) +    
    stat_boxplot(geom ='errorbar', width = 0.2) + 
    geom_boxplot(outlier.shape = NA) +
    geom_signif(test = "wilcox.test", 
                comparisons = list(c("PBNC", "CAP"),
                                   c("PBNC", "CBNP"),
                                   c("CBNP", "CAP")),
                vjust = 0,
                textsize = 4,
                size = .5,
                step_increase = .08,
                color="black") +
    theme_minimal()+
    theme_bw()+
    ylab("Log2 Distance to Annotation")+
    xlab("") +
    scale_fill_manual(name="Boundary Region",
                      values=c("green",
                               "red",
                               "blue"))+
    scale_color_manual(values=c("green",
                               "red",
                               "blue")) +
    guides(color=FALSE, linetype=FALSE)+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45,
                                     hjust = 1),
          axis.text.y = element_text(size = 15),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          strip.text.x = element_text(size = 15),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=15),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")
```
